A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
New last paragraph

It would be interesting to see whether these techniques are more broadly
applicable. Most obviously, we could solve the induced subgraph isomorphism
problem in the same way (and with nearly no changes to the code), but we could
not solve the non-induced version. However, we suspect that some other problems
may have a similar branching structure which would also benefit from a
different domain store representation.

>>>>

It would be interesting to see whether these techniques are more broadly
applicable---we suspect that some other problems may have a similar branching
structure which would also benefit from a different domain store
representation. Most obviously, we could solve the induced subgraph isomorphism
problem in the same way (and with nearly no changes to the code), and our
connected variant shows that certain side constraints can also be handled.
However, we cannot solve the non-induced subgraph isomorphism this way, nor can
we handle certain richer labelling schemes such as those used in temporal
subgraph isomorphism \citep{DBLP:conf/asunam/RedmondC13}.
